---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

`"binomial"` is a package that provides functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

* The function `bin_choose()` calculates the number of combinations in which k successes can occur in n trials.
* The function `bin_probability()` can calculate probabilities of getting certain successes in certain trials.
* The function `bin_distribution()` returns a data frame with the probability distribution: sucesses in the first column, probability in the second column.
* The function `bin_cumulative()` calculates both the probability distribution and the cumulative probabilities
* The function `bin_variable()` creates an object of class “binvar”
* The functions `bin_mean()`, `bin_variance()`, `bin_mode()`, `bin_skewness()`, `bin_kurtosis()` calculate the summary measures.
* `plot.bincum()` method for a `"bincum"` object to graph the cumulative distribution
* `plot.bindis()` method for a `"bindis"` object to graphs a barplot to display
the probability histogram
* `print.binvar()` method for a `"binvar"` object to nicely print the content
* `summary.binvar()` method for a `"binvar"` object to get a full summary description
* `"print.summary.binvar()"` method for a `"summary.binvar"` object to nicely print the contents

## Motivation

This package has been developed to provides functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

## Installation

Install the development version from GitHub via the package `"devtools"`:
```{r}
# development version from GitHub:
#install.packages("devtools") 
# install "cointoss" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-danzhaozju/workout3/binomial")
# install "cointoss" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-danzhaozju/workout3/binomial", build_vignettes = TRUE)
```  

## Usage
```{r}
library(binomial)

bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)

# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)

# probabilities of getting 2 or less successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)

# 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)

# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)

# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)

# binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)

# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)

var1 = bin_variable(5,0.5)

bin1 <- bin_variable(trials = 10, p = 0.3)
bin1

bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1

bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

